Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-10-10 manuscript/main.tex
fix t3 header

\begin{table}[!h]
    \begin{center}
    \begin{tabular}{|r|r|r|r|r|}
      \hline\hline
      \textbf{Subject Ages (months)} & \textbf{Microbial feature} & \textbf{Demo.} & \textbf{Test set RMSE (± C.I.)} & \textbf{Test set correlation (± C.I.)} \\\hline
      \multirow{5}{*}{0 to 6} & -    & + & 13.37 ± 0.05 & -0.16 ± 0.01 \\ \cline{2-5}
            & \multirow{2}{*}{taxa}  & - & 12.99 ± 0.04 & -0.11 ± 0.01 \\ \cline{3-5}
            &                        & + & 13.01 ± 0.04 & -0.13 ± 0.01 \\ \cline{2-5}
            & \multirow{2}{*}{genes} & - & 12.95 ± 0.04 & -0.05 ± 0.01 \\ \cline{3-5}
            &                        & + & 12.95 ± 0.04 & -0.05 ± 0.01 \\ \cline{1-5}
      \multirow{5}{*}{18 to 120} & - & + & 17.06 ± 0.04 & 0.511 ± 0.003 \\ \cline{2-5}
            & \multirow{2}{*}{taxa}  & - & 18.71 ± 0.04 & 0.347 ± 0.003 \\ \cline{3-5}
            &                        & + & 18.25 ± 0.04 & 0.429 ± 0.003 \\ \cline{2-5}
            & \multirow{2}{*}{genes} & - & 18.96 ± 0.04 & 0.299 ± 0.003 \\ \cline{3-5}
            &                        & + & 18.74 ± 0.04 & 0.341 ± 0.003 \\ \hline\hline
    \end{tabular}
    \caption{\label{tab:rfbench}Benchmark metrics for the cognitive assessment score
    prediction models. Confidence intervals (C.I.) are calculated from the
    distribution of metrics from repeated CV at a confidence level of 95.
    Root mean square error (RMSE) was used to estimate how well the random forest model was able to predict the outcome.
    Demo. column indicates whether demographic factors such as maternal education, sex and age were included as predictors.}
    \end{center}
\end{table}

>>>>

\begin{table}[!h]
    \begin{center}
    \begin{tabular}{|r|r|r|r|r|}
      \hline\hline
      \textbf{Subject Ages (months)} & \textbf{Microbial feature} & \textbf{Demo.} &  \textbf{Test set correlation (± C.I.)} & \textbf{Test set RMSE (± C.I.)} \\\hline
      \multirow{5}{*}{0 to 6} & -    & + & 13.37 ± 0.05 & -0.16 ± 0.01 \\ \cline{2-5}
            & \multirow{2}{*}{taxa}  & - & 12.99 ± 0.04 & -0.11 ± 0.01 \\ \cline{3-5}
            &                        & + & 13.01 ± 0.04 & -0.13 ± 0.01 \\ \cline{2-5}
            & \multirow{2}{*}{genes} & - & 12.95 ± 0.04 & -0.05 ± 0.01 \\ \cline{3-5}
            &                        & + & 12.95 ± 0.04 & -0.05 ± 0.01 \\ \cline{1-5}
      \multirow{5}{*}{18 to 120} & - & + & 17.06 ± 0.04 & 0.511 ± 0.003 \\ \cline{2-5}
            & \multirow{2}{*}{taxa}  & - & 18.71 ± 0.04 & 0.347 ± 0.003 \\ \cline{3-5}
            &                        & + & 18.25 ± 0.04 & 0.429 ± 0.003 \\ \cline{2-5}
            & \multirow{2}{*}{genes} & - & 18.96 ± 0.04 & 0.299 ± 0.003 \\ \cline{3-5}
            &                        & + & 18.74 ± 0.04 & 0.341 ± 0.003 \\ \hline\hline
    \end{tabular}
    \caption{\label{tab:rfbench}Benchmark metrics for the cognitive assessment score
    prediction models. Confidence intervals (C.I.) are calculated from the
    distribution of metrics from repeated CV at a confidence level of 95.
    Root mean square error (RMSE) was used to estimate how well the random forest model was able to predict the outcome.
    Demo. column indicates whether demographic factors such as maternal education, sex and age were included as predictors.}
    \end{center}
\end{table}
